Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-15 index.Rmd
tool deployment

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# need this to avoid loading the R libraries when the tool is deployed on shinyapps (needs to be 1 when run localy, 1 when deployed on a shinyapps server)

@@

if(run_shiny_tool) {
  library(googleVis)
  library("shiny")
  library("reshape2")  
  library("ggplot2")
  # Why are these not found when deployed?!
  library("shiny") 
  library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")

  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  #library("reshape")
  library("ggplot2")
}

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
shinyApp(
  ui = fluidPage(
    fluidRow(
      column(2,
             conditionalPanel(
               condition = "!$('makeReport').hasClass('shiny-busy')",
               actionButton("makeReport","Generate Report (Work in Progress)",icon=icon("file"))
             )
      ),
      column(4,
             conditionalPanel(
               condition = "!$('makeReport').hasClass('shiny-busy')",
               uiOutput("downloadButton")
               #downloadButton("downloadReport", "Download Report")
             )
      )
    ),
    busyIndicator("Please wait while we prepare the report ...",wait = 0)
  ),
  server = function(input, output) {
    output$download_button <- renderUI({
      downloadButton("downloadReport", "Download Results")
    })
    makeReportAction <- eventReactive(input$makeReport, {
      #Create the pdf here
      #Sys.sleep(1);return()
      #first check if we didn't already create a paper with these parameters, if so, load from cache
      #filename <- paste("reports/")
      #file.exists()
      tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
      newinput <- list()
      for(i in tosave) {
        newinput[[i]] <- input[[i]]
      }
      # Not yet available
      #knitr::knit2pdf("report.Rnw",envir=globalenv())
    })
    output$downloadButton <- renderUI({
      makeReportAction() #only appear after first click on generate
      downloadButton("downloadReport", "Download Report")
    })
    output$downloadReport <- downloadHandler(
      filename = "report.pdf",
      content = function(file) {
        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
        file.rename(normalizePath('report.pdf'), file)
      }
    )
  },
  options = list(height = 120,width=800)
)

>>>>

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# need this to avoid loading the R libraries when the tool is deployed on shinyapps (needs to be 0 when run localy, 1 when deployed on a shinyapps server)

@@

if(!run_shiny_tool) {
  library(googleVis)
  library("shiny")
  library("reshape2")  
  library("ggplot2")
  # Why are these not found when deployed?!
  library("shiny") 
  library("shinysky") #  devtools::install_github("AnalytixWare/ShinySky")

  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  #library("reshape")
  library("ggplot2")
} #else{
  #install.packages("Rcpp")
#}

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
shinyApp(
  ui = fluidPage(
    fluidRow(
      column(2,
             conditionalPanel(
               condition = "!$('makeReport').hasClass('shiny-busy')",
               actionButton("makeReport","Generate Report (Work in Progress)",icon=icon("file"))
             )
      ),
      column(4,
             conditionalPanel(
               condition = "!$('makeReport').hasClass('shiny-busy')",
               uiOutput("downloadButton")
               #downloadButton("downloadReport", "Download Report")
             )
      )
    ),
    busyIndicator("Please wait while we prepare the report ...",wait = 0)
  ),
  server = function(input, output) {
    output$download_button <- renderUI({
      downloadButton("downloadReport", "Download Results")
    })
    makeReportAction <- eventReactive(input$makeReport, {
      #Create the pdf here
      #Sys.sleep(1);return()
      #first check if we didn't already create a paper with these parameters, if so, load from cache
      #filename <- paste("reports/")
      #file.exists()
      #tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
      #newinput <- list()
      #for(i in tosave) {
      #  newinput[[i]] <- input[[i]]
      #}
      # Not yet available
      #knitr::knit2pdf("report.Rnw",envir=globalenv())
    })
    output$downloadButton <- renderUI({
      makeReportAction() #only appear after first click on generate
      downloadButton("downloadReport", "Download Report")
    })
    output$downloadReport <- downloadHandler(
      filename = "report.pdf",
      content = function(file) {
        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
        file.rename(normalizePath('report.pdf'), file)
      }
    )
  },
  options = list(height = 120,width=800)
)
